A survey of HTTP caching implementations on the open Semantic Web

### 2015-03-11 sanity/paper1.tex
Make a section of validity
git-svn-id: https://svn.ifi.uio.no/repos/users/kjekje-phd@1062 43ef1190-90fd-4dd7-a769-d0121f02b80e

A key challenge to the validity of the survey is biases that may be
introduced by the coverage and then the data reduction. The breadth of
the Semantic Web is derived mainly from the BTC2014 crawl. While
LODstats\footnote{\url{http://stats.lod2.eu/}} has presently seen an
order of magnitude more triples, the number of error-free datasets
were at the time of this writing 4442. We work under the assumption
that cache headers are set mostly on a per-host basis, and if this
assumption is valid, sampling a URL per host is sufficient. LODstats
do not report per-host statistics, but often one host will host
several datasets. Another recent crawl was reported by
\cite{stateoflod2014}. It is not clear how many hosts were crawled, but the
number of triples in the crawl is much smaller than that of
BTC2014. It is therefore a fair assumption that BTC2014 fairly well
represent the breadth of the Semantic Web, momentarily at least.

As for the coverage of vocabularies, we realize that LODstats might
have been a better source, but we have been able to select the most
important, and not far inferior in number. The number of SPARQL
endpoints found in SPARQLES is larger than LODstats, and we also
looked for further endpoints both in the BTC2014 and our own crawl,
finding only a few. If endpoints went underdiscovered, then there is a
discovery problem that is beyond this survey to rectify.

The data reduction that was subsequently done was mainly done to
eliminate errors. We have not investigated biases that may be
introduced by discarding momentarily dysfunctional parts of the
Semantic Web, but we investigated whether the freshness lifetimes
reported in the case of certain errors were distributed differently
from those that returned a valid response, the companion technical
report \cite{kjernsmo_add_survey_2015}. We found that they were, but
we have assumed that this is due to that errors are configured to be
cached differently, which we know from experience is common
practice. The following analysis is based on valid responses.

>>>>

\subsection{Challenges to validity}

Key challenges to the validity of the survey are biases that may be
introduced by the coverage and then the data reduction. The breadth of
the Semantic Web is derived mainly from the BTC2014 crawl. While
LODstats\footnote{\url{http://stats.lod2.eu/}} has presently seen an
order of magnitude more triples, the number of error-free datasets
were at the time of this writing 4442. We work under the assumption
that cache headers are set mostly on a per-host basis, and if this
assumption is valid, sampling a URL per host is sufficient. LODstats
do not report per-host statistics, but often one host will host
several datasets. Another recent crawl was reported by
\cite{stateoflod2014}. It is not clear how many hosts were crawled, but the
number of triples in the crawl is much smaller than that of
BTC2014. It is therefore a fair assumption that BTC2014 fairly well
represent the breadth of the Semantic Web, momentarily at least.

As for the coverage of vocabularies, we have verified that all
resolveable vocabularies in LODstats that are found in more than 10
datasets are visited, and it is not far inferior in number to
LODstats. The number of SPARQL endpoints found in SPARQLES is larger
than LODstats, and we also looked for further endpoints both in the
BTC2014 and our own crawl, finding only 18. If endpoints went
underdiscovered, then there is a discovery problem that is beyond this
survey to rectify.

The data reduction that was subsequently done was mainly done to
eliminate errors. We have not investigated biases that may be
introduced by discarding momentarily dysfunctional parts of the
Semantic Web, but we investigated whether the freshness lifetimes
reported in the case of certain errors were distributed differently
from those that returned a valid response, see the companion technical
report \cite{kjernsmo_add_survey_2015}. We found that they were, but
we have assumed that this is due to that errors are configured to be
cached differently, which we know from experience is common
practice. The following analysis is based on valid responses.
